Internal Gravity Wave Breaking in White Dwarf Binaries

### 2019-07-24 writeups/paper.tex
ugh
check in new files, stash

@@

Finally, we may be interested in the power spectrum of the transmitted
horizontal momentum flux. Define:
\begin{align}
    \tilde{S}_>(k_x, t) = \abs{
        \int\limits_0^{L_x} e^{ik_xx}\hat{S}_>(x, z_c - \Delta z, t)\;\mathrm{d}x}
            \label{eq:sfft_above},\\
    \tilde{S}_<(k_x, t) = \abs{
        \int\limits_0^{L_x} e^{ik_xx}\hat{S}_<(x, z_c + \Delta z, t)\;\mathrm{d}x}.
            \label{eq:sfft_below}
\end{align}
These values are plotted in \autoref{fig:nl_fft}. Note that we expect
$\tilde{S}_<(0, t) = S_<(t) = S_i(t) + S_d(t)$ and the same for $\tilde{S}_>$.
This is rather accurate for $\tilde{S}_<$ but less so for $\tilde{S}_>$; this is
since $S_>(t)$ decays very rapidly above $z_c$. Note furthermore that at later
times, the transmitted flux increases, per expectation, and shifts towards
higher $k_x$. Repeating this plot at higher viscosities shows significantly
lower $\tilde{S}_>$, showing that the $k_x$ of the transmitted waves still
changes greatly at the highest $\mathrm{Re}$ we are able to probe. Finally, note
that the area under $\tilde{S}$ changes with time; this is okay since we are
measuring $S$ at constant position, and different $k_x$ components of $S$ will
translate at their separate group velocities.

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{plots/nl_fft.png}
    \caption{The power spectrum of the horizontal momentum flux at fixed
    distances below and above critical layer $z_c$ at certain times $t$ for
    simulation \texttt{0p5\_shres}. \autoref{eq:sfft_above} and
    \autoref{eq:sfft_below} are depicted here, with $\tilde{S}_<$ in solid lines
    and $\tilde{S}_>$ in dashed lines. Note that there is more incident flux
    than transmitted, and that transmitted flux roughly increases over
    time.}\label{fig:nl_fft}
\end{figure}

@@

equations as simulated in Dedalus:

>>>>

% cp ../sims/agg.png plots
% cp ../sims/2d_3_final/snapshots_lin_0_masked/f_amps.png plots/lin_amps.png
% cp ../sims/2d_3_final/snapshots_lin_0_masked/fluxes.png plots/lin_fluxes.png
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_amps.png plots/nl_f_amps.png
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/fluxes.png plots/nl_fluxes.png
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_refl.png plots/nl_f_refl.png
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/f_ri.png plots/nl_f_ri.png
% cp ../sims/2d_4_fourier/snapshots_yubo_nu1_vhres/front.png plots/nl_front.png

@@

% Finally, we may be interested in the power spectrum of the transmitted
% horizontal momentum flux. Define:
% \begin{align}
%     \tilde{S}_>(k_x, t) = \abs{
%         \int\limits_0^{L_x} e^{ik_xx}\hat{S}_>(x, z_c - \Delta z, t)\;\mathrm{d}x}
%             \label{eq:sfft_above},\\
%     \tilde{S}_<(k_x, t) = \abs{
%         \int\limits_0^{L_x} e^{ik_xx}\hat{S}_<(x, z_c + \Delta z, t)\;\mathrm{d}x}.
%             \label{eq:sfft_below}
% \end{align}
% These values are plotted in \autoref{fig:nl_fft}. Note that we expect
% $\tilde{S}_<(0, t) = S_<(t) = S_i(t) + S_d(t)$ and the same for $\tilde{S}_>$.
% This is rather accurate for $\tilde{S}_<$ but less so for $\tilde{S}_>$; this is
% since $S_>(t)$ decays very rapidly above $z_c$. Note furthermore that at later
% times, the transmitted flux increases, per expectation, and shifts towards
% higher $k_x$. Repeating this plot at higher viscosities shows significantly
% lower $\tilde{S}_>$, showing that the $k_x$ of the transmitted waves still
% changes greatly at the highest $\mathrm{Re}$ we are able to probe. Finally, note
% that the area under $\tilde{S}$ changes with time; this is okay since we are
% measuring $S$ at constant position, and different $k_x$ components of $S$ will
% translate at their separate group velocities.

@@

equations as simulated in Dedalus: [TODO update w/ mask]
